
\cvsection{Education}
\cvevent{Computer Science - 4.0 GPA}{University of Toronto}{ September 2022 -- Currently}{}
\cvevent{IB Diploma}{The York School}{ September 2020 - May 2022 }{}
% \cvachievement{\faTrophy}{}{Received accolades at Atos for Best Performance in team.}
% \cvachievement{\faTrophy}{}{Received Best Debut Award at Atos. }
% %\divider
% \cvachievement{\faInstitution}{}{Won 2nd Consolation Prize for paper presented on Cognitive Radio Networks.}
% %\divider
% \cvachievement{\faGraduationCap}{}{Got Selected in "Exclusive Scholar Program" during undergrad.}
% %\divider
% \cvachievement{\faDollar}{}{Awarded with Narotam Sekhsaria Foundation Scholarship}
%\cvsection{Strengths}

%\cvtag{Hard-working (18/24)} 
%\cvtag{Persuasive}
%\cvtag{Motivator \& Leader}

%\divider\smallskip

%\cvtag{UX}
%\cvtag{Mobile Devices \& Applications}
%\cvtag{Product Management \& Marketing}


%\divider

%\cvevent{B.S.\ in Symbolic Systems}{Stanford University}{Sept 1993 -- June 1997}{}

\cvsection{Personal Projects}
All projects can be found on my GitHub, linked in the header.

\smallskip
\smallskip
\cvproject{Pricing Bitcoin Call Options}
\begin{itemize}
\item Pricing european-style Bitcoin call options with a modified version of the
Black-Scholes model. Read more here: https://github.com/alexrosen45/bitcoin\_call\_options\_-public-
\end{itemize}
\smallskip
\smallskip
\cvproject{Snacker}
\begin{itemize}
\item Snacker is a real-time food truck locator app (Android and iOS). Building Snacker using the Flutter framework with GCP allowed me to gain enough experience and confidence to work as a full-stack developer.
\item The app reached \textasciitilde 1000 downloads, and you can check out the (deprecated) version here: https://sites.google.com/view/snacker-download?pli=1
\end{itemize}
\smallskip
\smallskip
\cvproject{Dogebot — Trading Bot}
\begin{itemize}
\item Dogebot is a Python powered trading bot used to analyse the price movements of Dogecoin
after Elon Musk tweets about it.
\end{itemize}
\smallskip
\smallskip
\cvproject{Personal Website version 2}
\begin{itemize}
\item A website for displaying my projects and contact information:
https://arpersonalwebsite.com/
\end{itemize}
\smallskip
\smallskip
\cvproject{COVID-19 Information App}
\begin{itemize}
\item An app that displays data using API's from Johns Hopkins and the World
Health Organization on relevant COVID-19 statistics for your area. It also
has information sections on FDA-approved vaccines and the latest local
or global COVID-19 news stories from trusted sources. This project was mostly
built using Java in Android Studio.
\end{itemize}
\cvproject{}